Biotic invasions reduce the manageability of pollination networks

### 2016-12-05 paper/EL-reviewer-comments-1.Rmd
some modifications to the methods

---
title: "Response to reviewer comments ELE-00738-2016"
date: "21 November 2016"
output: pdf_document
---

@@

The paragraph on lines 50-62 cites papers published no earlier than 2011. However, to support the following argument "Despite these advances, the link between the structure of complex networks and our ability to manage and conserve them is still ambiguous", the authors cite a paper that predates all of them (Tylianakis et al. 2010). The paper in question highlights practical challenges to conservation; many if not all of them remain today (which I suspect is the authors' argument). I suggest the authors revise the text to make the contribution of this reference clear.

Comment 3
Lines 95-97: "The number of nodes necessary to fully control a complex network can be calculated by counting the number of unmatched nodes in the network's maximum matching (Liu et al. 97 2011)."

This statement must be contextualized by the assumed nature of the dynamical relationships in this framework. It therefore seems to me that this statement should be preceded by a discussion of those details (indeed, the authors argue that this is necessary in the Introduction, on lines 48-49).

Furthermore, the authors need to discuss the appropriateness of this framework to ecological systems. The input control signals that drive even relatively simple networks to specified states can be very sensitive to initial conditions and complicated (indeed, they usually aren't calculated at all). How can a control scheme be implemented even in principle if nodes represent species populations and a control signal calls for a fractional change in a node state variable over the course of minutes? Furthermore, how do the authors interpret the methods by which cycles are controlled in linear control theory (see e.g. doi 10.1126/science.1242063 and its supplementary material) in the context of ecological management? How frequent are cycles in the authors' ecological networks?

I should emphasize that I am a fan of control theory and I think it is interesting to apply it as the authors do in this ms. However, the caveats that come along with the points I outline above need to be made clear for the reader.

The authors might be interested in doi 10.1063/1.4931570 for a discussion of some relevant ideas.

Comment 4
Lines 101-103: "(ii) the sum of the weights of the matched links—known as matching weight—is the largest possible among all possible matchings of that size (West 2001)."

The authors go on to cite Liu et al. 2011, but that report (and many others cited in the present ms) considers "structural controllability", which assumes binary edge weights (i.e., they exist or they do not). Is condition (ii) appropriate here? If so, why? The authors get at this later in the ms (lines 145-152, where it looks as if edges are indeed binarized), but for readers familiar with the structural control literature, there is room for confusion as they come to this point in the ms. This may be mitigated as the authors address my comment 3, but it seems appropriate for me to raise this point explicitly as well.

Comment 5
When defining n_d on line 119, it is more accurate to say that it is the "minimum number" of species needed to gain full control.

Comment 6
Lines 132-133: "...we therefore call driver species those that are identified as being a superior node in all possible matchings..."
I have several comments here. First, shouldn't this be "all possible maximum matchings"?

@@

Comment 7
The approach described in lines 145-152 would be clearer if the authors included a figure demonstrating each step for a simple network.

Comment 8
Lines 173-176: "To do so, we calculated the maximum matching of the corresponding pollination network, and estimated the minimum proportion of species that need directed interventions to fully control the species abundances in the community." Why is this an estimate? The number of species that need to be directly controlled can be determined unambiguously.

Comment 9
It seems to me that the number of interactions would also be an interesting factor to consider in the statistical analysis (discussed beginning on line 213).

Comment 10
Lines 225-228: "Previous research indicates a direct link between a network's degree distribution and the number of nodes necessary to fully control it (Liu et al. 2011), but the strength and applicability of this relationship has not been tested for in weighted ecological networks."

@@

Comment 11
It seems useful to mention the typical size of the networks at the beginning of the results, if not earlier. In addition, the fact that the mean value of m is 0.37 means that roughly two thirds of the species in these communities need to be directly controlled, at least according to this modeling framework. It seems to me that this merits explicit comment in the Discussion.

@@

Comment 12
Figure 3 should show the distributions of m as well as the adjusted value of m. I suggest also providing more detail about how the adjusted value is calculated (in the current version there is one technical sentence that non-experts will not be able to follow).

Comment 13
In Appendix S2 (referenced in the ms on lines 205-208), the authors state that the relative number of driver species, while different for the approaches there discussed, are not significantly different from one another. However, the statistical test used is a Spearman correlation coefficient, which does not measure the difference in e.g. population means but rather the extent to which their relationship is monotonic.

@@

Referee: 2

Comments for the Authors
General comments
This manuscript proposes to apply the methods published in previous papers (e.g. Liu et al, Nature 2011) on the controllability of complex systems to invaded pollination networks. Note that controllability is rebranded “manageability” (unless it has a different meaning in this paper?). The manuscript also proposes to identify the nodes to manage or driver species. This is a fascinating area of research.
Performing a controllability study on ten pairs of uninvaded and invaded plant-pollinator networks, the main finding is that invaded networks require a higher number of nodes to control than their non-invaded counterpart and invasive plants were driver species in all studied communities.
The study is scientifically sound. However the manuscript is dense and difficult to read. In particular the section Theoretical framework and its subsection are confusing and should be merged with the Methods section. The discussion should be strengthen.
In its current form, it is unlikely that readers will be able to understand or replicate the research presented – which is a shame considering the authors went through a lot of trouble to apply a control theory study in an ecological context. An overall simplification of the language/sentences and jargon used will increase the readability of this manuscript. Ruths (2014, Science) and Liu (2011, Nature) are doing a better job at explaining maximum matching, driver nodes and the overall challenge of controllability.
Specific comments
1)      Consider being more specific in your abstract.
2)      L74 “we _expand_ previous theory of the control of complex systems to an ecological context”. Do you mean apply? Please clarify your contribution without ambiguity.
3)      Section Manageability (L94).
a.      Please first define manageability before maximum matching.
b.      The maximum matching paragraph is difficult to understand. Reword.
4)      Section Relative importance (L121).
a.      It seems that the abstract refers to this section as being a novel way to identify communities’ driver species. However it is very unclear that this is a novel contribution. Please clarify in the text and provide details in supplementary information. It is also unclear from the Methods section.
5)      Discussion:
a.      McDonaldMadden et al (2016) actually show that network metrics are not useful to prioritise the management of foodweb, i.e. to determine which species should be managed first (if required). Please edit current text and analyse differences with your work.
b.      Please provide some insight into how your method/analysis/results would differ for non- pollinator invaded networks.
c.      Please discuss the caveats of your approach. I suggest moving some of the statistical analyses in sup info if word limit is an issue.

6)      The maximum matching algorithm is computationally expensive as noted by the authors. In Ruths & Ruths (2014) the authors come with an interesting alternative to calculate the minimum number of independent controls (driver species) using only the number of source nodes, external dilation points and internal dilation points; and a heuristic using source and sink nodes. What is the profile of the pollinator networks studied? Would the Ruths & Ruths approach be an easier way of reaching the same conclusions? Would it bring complementary information?
7)      A few typos in main text and sup info.
8)      Is there a compelling reason to change controllability to “manageability”? Walters did the same thing with “adaptive management” in lieu of “adaptive control”.
30 years later, no one remembers where “adaptive management” originally came from and it has become a keyword in ecology. As a result, ecologists have been cut from the theoretical advances in control theory and most often have no clue that these are the same thing.

Referee: 3

Comments for the Authors
In this work Cagua et al apply tools rooted in control theory to ecological networks and discuss how this approach could be used for management of natural systems, with emphasis on the effects of invasive species. This is an exciting work. It presents to ecologists a novel way of studying the relationship between topology and dynamics that is less dependent (when compared to other methods) on particular choices about how dynamics are modeled. The authors illustrate the potential of this approach by exploring how invasive species change system dynamics and manageability. My only concern about this manuscript is that the authors need to be more careful and more explicit about some limitations of this approach and the generality of their results, specially considering the implications of their results for management.

@@

>>>>

---
title: "Response to reviewer comments ELE-00738-2016"
date: "21 November 2016"
output: pdf_document
bibliography: references.bib
---

@@

- The paragraph on lines 50-62 cites papers published no earlier than 2011. However, to support the following argument "Despite these advances, the link between the structure of complex networks and our ability to manage and conserve them is still ambiguous", the authors cite a paper that predates all of them (Tylianakis et al. 2010). The paper in question highlights practical challenges to conservation; many if not all of them remain today (which I suspect is the authors' argument). I suggest the authors revise the text to make the contribution of this reference clear.

    *Accepted; changed. We revised the text to better reflect the contribution of @Tylianakis2010 at the same time we added a reference to a more recent paper by @Kaiser-Bunbury2015 who explicitly deals with oportunities, limitations and implications of applying network metrics in conservation science.*

- Lines 95-97: "The number of nodes necessary to fully control a complex network can be calculated by counting the number of unmatched nodes in the network's maximum matching (Liu et al. 97 2011)." This statement must be contextualized by the assumed nature of the dynamical relationships in this framework. It therefore seems to me that this statement should be preceded by a discussion of those details (indeed, the authors argue that this is necessary in the Introduction, on lines 48-49).

- Furthermore, the authors need to discuss the appropriateness of this framework to ecological systems. The input control signals that drive even relatively simple networks to specified states can be very sensitive to initial conditions and complicated (indeed, they usually aren't calculated at all). How can a control scheme be implemented even in principle if nodes represent species populations and a control signal calls for a fractional change in a node state variable over the course of minutes? Furthermore, how do the authors interpret the methods by which cycles are controlled in linear control theory (see e.g. doi 10.1126/science.1242063 and its supplementary material) in the context of ecological management? How frequent are cycles in the authors' ecological networks? I should emphasize that I am a fan of control theory and I think it is interesting to apply it as the authors do in this ms. However, the caveats that come along with the points I outline above need to be made clear for the reader. The authors might be interested in doi 10.1063/1.4931570 for a discussion of some relevant ideas.

    * Acepted; changed.*

- Lines 101-103: "(ii) the sum of the weights of the matched links—known as matching weight—is the largest possible among all possible matchings of that size (West 2001)." The authors go on to cite Liu et al. 2011, but that report (and many others cited in the present ms) considers "structural controllability", which assumes binary edge weights (i.e., they exist or they do not). Is condition (ii) appropriate here? If so, why? The authors get at this later in the ms (lines 145-152, where it looks as if edges are indeed binarized), but for readers familiar with the structural control literature, there is room for confusion as they come to this point in the ms. This may be mitigated as the authors address my comment 3, but it seems appropriate for me to raise this point explicitly as well.

- When defining n_d on line 119, it is more accurate to say that it is the "minimum number" of species needed to gain full control.

- Lines 132-133: "...we therefore call driver species those that are identified as being a superior node in all possible matchings..."
I have several comments here. First, shouldn't this be "all possible maximum matchings"?

@@

- The approach described in lines 145-152 would be clearer if the authors included a figure demonstrating each step for a simple network.

- Lines 173-176: "To do so, we calculated the maximum matching of the corresponding pollination network, and estimated the minimum proportion of species that need directed interventions to fully control the species abundances in the community." Why is this an estimate? The number of species that need to be directly controlled can be determined unambiguously.

- It seems to me that the number of interactions would also be an interesting factor to consider in the statistical analysis (discussed beginning on line 213).

- Lines 225-228: "Previous research indicates a direct link between a network's degree distribution and the number of nodes necessary to fully control it (Liu et al. 2011), but the strength and applicability of this relationship has not been tested for in weighted ecological networks."

@@

- It seems useful to mention the typical size of the networks at the beginning of the results, if not earlier. In addition, the fact that the mean value of m is 0.37 means that roughly two thirds of the species in these communities need to be directly controlled, at least according to this modeling framework. It seems to me that this merits explicit comment in the Discussion.

@@

- Figure 3 should show the distributions of m as well as the adjusted value of m. I suggest also providing more detail about how the adjusted value is calculated (in the current version there is one technical sentence that non-experts will not be able to follow).

- In Appendix S2 (referenced in the ms on lines 205-208), the authors state that the relative number of driver species, while different for the approaches there discussed, are not significantly different from one another. However, the statistical test used is a Spearman correlation coefficient, which does not measure the difference in e.g. population means but rather the extent to which their relationship is monotonic.

@@

## Referee 2

This manuscript proposes to apply the methods published in previous papers (e.g. Liu et al, Nature 2011) on the controllability of complex systems to invaded pollination networks. Note that controllability is rebranded “manageability” (unless it has a different meaning in this paper?). The manuscript also proposes to identify the nodes to manage or driver species. This is a fascinating area of research.
Performing a controllability study on ten pairs of uninvaded and invaded plant-pollinator networks, the main finding is that invaded networks require a higher number of nodes to control than their non-invaded counterpart and invasive plants were driver species in all studied communities.
The study is scientifically sound. However the manuscript is dense and difficult to read. In particular the section Theoretical framework and its subsection are confusing and should be merged with the Methods section. The discussion should be strengthen.
In its current form, it is unlikely that readers will be able to understand or replicate the research presented – which is a shame considering the authors went through a lot of trouble to apply a control theory study in an ecological context. An overall simplification of the language/sentences and jargon used will increase the readability of this manuscript. Ruths (2014, Science) and Liu (2011, Nature) are doing a better job at explaining maximum matching, driver nodes and the overall challenge of controllability.

- Consider being more specific in your abstract.

- L74 “we expand previous theory of the control of complex systems to an ecological context”. Do you mean apply? Please clarify your contribution without ambiguity.

    *Acepted; changed. The sentence now reads "To bridge this gap, we propose methods to apply previous theory on the control of complex systems into an ecological context and implement them in empirical data"*

- Section Manageability (L94). Please first define manageability before maximum matching. Also, the maximum matching paragraph is difficult to understand. Reword.

- Section Relative importance (L121). It seems that the abstract refers to this section as being a novel way to identify communities’ driver species. However it is very unclear that this is a novel contribution. Please clarify in the text and provide details in supplementary information. It is also unclear from the Methods section.

- Discussion. McDonaldMadden et al (2016) actually show that network metrics are not useful to prioritise the management of foodweb, i.e. to determine which species should be managed first (if required). Please edit current text and analyse differences with your work.

- Discussion. Please provide some insight into how your method/analysis/results would differ for non- pollinator invaded networks.

- Discussion. Please discuss the caveats of your approach. I suggest moving some of the statistical analyses in sup info if word limit is an issue.

- The maximum matching algorithm is computationally expensive as noted by the authors. In Ruths & Ruths (2014) the authors come with an interesting alternative to calculate the minimum number of independent controls (driver species) using only the number of source nodes, external dilation points and internal dilation points; and a heuristic using source and sink nodes. What is the profile of the pollinator networks studied? Would the Ruths & Ruths approach be an easier way of reaching the same conclusions? Would it bring complementary information?

- A few typos in main text and sup info.

- Is there a compelling reason to change controllability to “manageability”? Walters did the same thing with “adaptive management” in lieu of “adaptive control”. 30 years later, no one remembers where “adaptive management” originally came from and it has become a keyword in ecology. As a result, ecologists have been cut from the theoretical advances in control theory and most often have no clue that these are the same thing.

## Referee 3

In this work Cagua et al apply tools rooted in control theory to ecological networks and discuss how this approach could be used for management of natural systems, with emphasis on the effects of invasive species. This is an exciting work. It presents to ecologists a novel way of studying the relationship between topology and dynamics that is less dependent (when compared to other methods) on particular choices about how dynamics are modeled. The authors illustrate the potential of this approach by exploring how invasive species change system dynamics and manageability. My only concern about this manuscript is that the authors need to be more careful and more explicit about some limitations of this approach and the generality of their results, specially considering the implications of their results for management.

@@

## References

### 2016-12-05 paper/manuscript.Rmd
some modifications to the methods

It is generally unknown how the disruptions caused by perturbations such as biotic invasions, affect our ability to manage ecological communities. 
Here, we expand current theory on the controllability of complex systems to quantitatively assess the theoretical (relative) manageability of ten pairs of uninvaded and invaded plant-pollinator communities.
Intriguingly, we found that invaded pollination networks might be more resilient than their uninvaded counterparts as they showed substantially lower levels of manageability.
We also developed theory to help identify each community's driver species—those most important to manage because of their disproportionate potential to affect the abundances of all other species. 
Remarkably, invasive plants were found to be driver species in every community in which they were found; their dominant position was generally underpinned by high asymmetry in the dependence of their interaction partners.
Our results provide a theoretical explanation for the known challenges associated with the restoration of invaded communities, and also provide insight into the design of informed management interventions.

*Shorter version*: 
It is generally unknown how the disruptions caused by perturbations like biotic invasions, affect our ability to manage ecological communities. 
Here, we expand current theory on the controllability of complex systems to assess the theoretical manageability of ten pairs of uninvaded and invaded plant-pollinator communities.
We found that invaded pollination networks might be more resilient than their uninvaded counterparts as they showed substantially lower manageability.
We also identify each community's driver species—those most important to manage because of their disproportionate potential to affect the abundances of all other species. 
Remarkably, invasive plants were found to be driver species in every community in which they were found; their dominant position was generally underpinned by high asymmetry in the dependence of their interaction partners.
Our results provide a theoretical explanation for the known challenges associated with the restoration of invaded communities, and also provide insight into the design of informed management interventions.

@@

Complex systems are characterised by non-linear relationships in which the whole is greater than the sum of its parts [@Jorgensen1998; @Levin1999; @Montoya2006].
Within community ecology, a complex systems approach has led to the development of a variety of analytical and simulation tools with which to understand, for example, the role of species when embedded in an intricate network of interactions [@Pascual2005; @Bascompte2009; @Stouffer2012]. 
The inherent complexity of nature, however, has hindered—or at least greatly complicated—our ability to find management solutions to the many problems ecological communities face. 
To overcome this obstacle, we require a framework that allow us to explain, predict, and manage ecological communities, particularly when they are faced with perturbations [@Sole2001; @Green2005].
Moreover, such a framework needs to be able to account for their complex structure, and the dynamics that determine the state of each species, and the community as a whole.

@@

Despite these advances, the link between the structure of complex networks and our ability to manage and conserve them is still ambiguous [@Tylianakis2010].
To complicate things further, biotic invasions—a major driver of global change—can induce dramatic changes on the patterns of interactions that determine the structure of ecological networks [@Baxter2004; @Tylianakis2008; @Ehrenfeld2010a]. 
Although understanding how differences in network structure before and after the invasion impact our ability to manage them presents a double challenge, it is a critical first step towards a fully informed recovery. 
Despite the apparent overlap, a control-theoretic perspective has not been widely adopted in an invasion context. 
This is perhaps because of a lack of appropriate methodological tools that can account for observed variation on the strength of interspecific effects that are characteristic of ecological networks [@Liu2011; @Isbell2013].

To bridge this gap, we expand previous theory of the control of complex systems to an ecological context.
We then use a set of ten pairs of uninvaded and invaded plant-pollinator communities to investigate the link between invasion, network structure and ecological management. 
We ask two specific questions framed in the context of a plant invasion.
First, we ask whether invaded networks have lower levels of manageability than their uninvaded counterparts; that is, whether they require a greater proportion of species to be managed to achieve the same level of control. 
Second, we ask whether some species are more important than others at driving the population dynamics of the community and which factors determine this importance. 
We focus on these particular applications for a variety of reasons. 
First, biotic invasions are known to produce tractable changes in the structure of ecological networks, and these changes can be particularly pronounced in mutualistic networks between plants and pollinators where biotic invasions have been shown to modify the strength of species interactions and the degree of network nestedness and connectivity [@Olesen2002; @Aizen2008; @Bartomeus2008; @Vila2009; @Traveset2013]. 
Second, plant-pollinator networks provide an ideal framework to answer these questions. 
On one hand, community networks that quantify relative levels of interaction are readily available. 
On the other, the bipartite nature of pollination networks makes it possible to simplify assumptions of how these interactions translate into interspecific effects.

## Theoretical framework

### Manageability

@@

Given a maximum matching, the link to network controllability has a largely intuitive basis. 
In control theory, a network is fully controllable when each node has a "superior", that is, an input that drives its dynamics. 
Consequently, each matched nodes can be controlled by the node pointing to it.
Unmatched nodes, on the other hand, have no superior in the network and must be directly controlled by external inputs [@Liu2011]. 
In an ecological context, these external inputs are what could be referred to as management interventions. 
Building on this analogy, systems that require a large number of external inputs are more difficult or costly to control. 
Therefore, the manageability *m* of a community can be approximated by the proportion of species on which we would need to apply management interventions in order to gain full control of the abundances of *all* species in the ecological community. This is given by $$m = 1- \frac{n_d}{s},$$ where *m* ranges between zero and one, *n~d~* is the number of species needed to gain full control and *s* is the total number of species in the community.

### Relative importance

@@

@@

### Community manageability

@@

#### Weighting & directing links

@@

#### Statistical analysis

@@

@@

      })
  })

>>>>

It is generally unknown how the disruptions caused by perturbations like biotic invasions affect our ability to manage ecological communities. 
Here, we expand theory on the controllability of complex systems to assess the theoretical manageability of ten pairs of uninvaded and invaded plant-pollinator communities. 
We found that invaded pollination networks appear more resilient than their uninvaded counterparts as they showed substantially lower manageability. 
We also introduce a novel way to identify communities’ driver species—those most important to manage because of their disproportionate potential to affect the abundances of all other species. 
Remarkably, we observed that invasive plants were driver species in every community in which they were found, and their dominant position was underpinned by the high asymmetry in the dependence of their interaction partners. 
Our results provide a theoretical explanation for the known challenges associated with the  restoration of invaded communities, and also provide insight into the design of informed management interventions.

@@

Complex systems are characterised by relationships in which the whole is often greater than the sum of its parts [@Jorgensen1998; @Levin1999; @Montoya2006].
Within community ecology, a complex systems approach has led to the development of a variety of analytical and simulation tools with which to understand, for example, the role of species when embedded in an intricate network of interactions [@Pascual2005; @Bascompte2009; @Stouffer2012]. 
The inherent complexity of nature, however, has hindered—or at least greatly complicated—our ability to find management solutions to the many problems ecological communities face. 
To overcome this obstacle, we require a framework that allow us to explain, predict, and manage ecological communities, particularly when they are faced with perturbations [@Sole2001; @Green2005].
Moreover, such a framework needs to be able to account for their complex structure, and the dynamics that determine the state of each species, and the community as a whole.

@@

Despite these advances, practical challenges to the conservation of interaction networks still persist [@Tylianakis2010] and the link between the structure of complex networks and our ability to manage and conserve them is still ambiguous [@Kaiser-Bunbury2015].
To complicate things further, biotic invasions—a major driver of global change—can induce dramatic changes on the patterns of interactions that determine the structure of ecological networks [@Baxter2004; @Tylianakis2008; @Ehrenfeld2010a]. 
Although understanding how differences in network structure before and after the invasion impact our ability to manage them presents a double challenge, it is a critical first step towards a fully informed recovery. 
Despite the apparent overlap, a control-theoretic perspective has not been widely adopted in an invasion context. 
This is perhaps because of a lack of appropriate methodological tools that can account for observed variation on the strength of interspecific effects that are characteristic of ecological networks [@Liu2011; @Isbell2013].

To bridge this gap, we propose methods to apply previous theory on the control of complex systems into an ecological context and implement them using empirical data.
Specifically we use a set of ten pairs of uninvaded and invaded plant-pollinator communities to investigate the link between invasion, network structure and ecological management. 
We ask two questions framed in the context of a plant invasion.
First, we ask whether invaded networks have lower levels of manageability than their uninvaded counterparts; that is, whether they require a greater proportion of species to be managed to achieve the same level of control. 
Second, we ask whether some species are more important than others at driving the population dynamics of the community and which factors determine this importance. 
We focus on these particular applications for a variety of reasons. 
First, biotic invasions are known to produce tractable changes in the structure of ecological networks, and these changes can be particularly pronounced in mutualistic networks between plants and pollinators where biotic invasions have been shown to modify the strength of species interactions and the degree of network nestedness and connectivity [@Olesen2002; @Aizen2008; @Bartomeus2008; @Vila2009; @Traveset2013]. 
Second, plant-pollinator networks provide an ideal framework to answer these questions. 
On one hand, community networks that quantify relative levels of interaction are readily available. 
On the other, the bipartite nature of pollination networks makes it possible to simplify assumptions of how these interactions translate into interspecific effects.

### Theoretical framework

Dynamical contstraints

#### Controlability

The structural controllability of a complex system can be approximated by the proportion of nodes to which we would need to apply external control input signals in order to gain full control of the state of all nodes in the network. 
This finding is based on the premise that a complex network behaves like a dynamical system in which the state of a given node can be potentially modified by altering state of any of the nodes pointing to it.
In an ecological community species populations can often be viewed as a function of the populations of the species they interact with.
This ability to treat communities as a network of coupled dynamic entities enables the application of control theory in ecological settings, hence provide an explicit link between network structure and managament applications.

Indeed, in an ecological context, external control input signals that modify the state of a node (a species' population) could be refered as management interventions.
Building on this analogy, systems that require a large number of external inputs are more difficult or costly to control. 
Therefore, the manageability of a community is inversely related to its controllability *c*. This is given by $$c = \frac{n_d}{s},$$ where *c* ranges between zero and one, *n~d~* is the minimum number of species to which management interventions are needed to gain full control, and *s* is the total number of species in the community.
Although the

systems, and hence where s
Ecological communities are a prime candidate
In an ecological context

@@

Given a maximum matching, the link to network controllability has a largely intuitive basis. 
In control theory, a network is fully controllable when each node has a "superior", that is, an input that drives its dynamics. 
Consequently, each matched nodes can be controlled by the node pointing to it.
Unmatched nodes, on the other hand, have no superior in the network and must be directly controlled by external inputs [@Liu2011].

In an ecological context, these external inputs are what could be referred to as management interventions. 
Building on this analogy, systems that require a large number of external inputs are more difficult or costly to control. 
Therefore, the manageability *m* of a community can be approximated by the proportion of species on which we would need to apply management interventions in order to gain full control of the abundances of *all* species in the ecological community. This is given by $$m = 1- \frac{n_d}{s},$$ where *m* ranges between zero and one, *n~d~* is the number of species needed to gain full control and *s* is the total number of species in the community.

#### Relative importance

@@

### Empirical data

@@

#### Community manageability

@@

##### Weighting & directing links

@@

##### Statistical analysis

@@

#### Relative importance of species

@@

      })
  }, .progress = "text")
